%% ================================================================
%% Appendix addendum: EW upper bound, falsification page,
%% and Colab reference
%% ================================================================

%% Already in Z11; this addendum goes into the Z12 comprehensive section
%% as subsection Z12.7

\subsection{Controlled 2-loop electroweak upper bound}
\label{sec:ew_bound}

The $W$-boson contribution to $m_p/m_e$ \emph{cancels} in the ratio:
both quarks and electrons carry $C_2(\mathrm{SU}(2))=3/4$, so
$\Delta C_W = 0$ at every loop order. This is the weak analog of the
electromagnetic $\alpha^1$-cancellation.

The surviving $Z$-boson correction enters at 2-loop (mixed QCD$\times$EW
diagram). Using the SFST 2-loop structure:
\begin{equation}\label{eq:ew_bound}
  \delta_{\mathrm{EW}}
  = \frac{\alpha_W}{4\pi}\cdot\Delta C_Z\cdot\frac{\alpha^2}{\sqrt{8}},
  \qquad
  \Delta C_Z = \frac{2(g_V^2\!+\!g_A^2)_u + (g_V^2\!+\!g_A^2)_d}{3}
    - (g_V^2\!+\!g_A^2)_e,
\end{equation}
where only the \emph{non-universal} vertex corrections (not absorbed into
the running of~$\alpha$) contribute. With
$\alpha_W/(4\pi)\approx 2.7\times 10^{-3}$ and $\Delta C_Z\approx 0.05$:
\begin{equation}\label{eq:ew_central}
  \delta_{\mathrm{EW}}
  \approx 2.7\times 10^{-3}\times 0.05\times 1.88\times 10^{-5}
  \approx 3\;\mathrm{ppb}
  \qquad(\text{range: }0.5\text{--}50\;\mathrm{ppb}).
\end{equation}
This is consistent with the current residual of $+2.3\,$ppb and below
experimental precision ($\sim\!6\,$ppb). The correction does \emph{not}
affect the sub-ppm claim.

Script: \texttt{ew\_2loop\_upper\_bound.py}.

%% ================================================================
\subsection{What would kill SFST: ten falsification criteria}
\label{sec:kill}

\begin{center}
\renewcommand{\arraystretch}{1.25}\small
\begin{tabular}{clp{3.2cm}p{3.8cm}}
\toprule
\# & \textbf{Criterion} & \textbf{Tolerance} & \textbf{Experiment / method}\\
\midrule
1 & $m_p/m_e \neq 6\pi^5(1+\alpha^2/\!\sqrt{8})$
  & $|\Delta|>0.01\,$ppm & Penning trap (BASE, ALPHATRAP)\\
2 & $\alpha$ (2-loop) $\neq$ experiment
  & $|\Delta\alpha/\alpha|>10^{-10}$ & Cs-133 interferometry\\
3 & $\Delta m_{n\text{-}p}\neq m_e(8/\pi-2\alpha)$
  & $|\Delta|>1000\,$ppm & neutron $\beta$-decay\\
4 & $c_2\notin [0.86,\;1.86]$
  & --- & derived from V1$\cap$V3\\
5 & $|W|\neq 6$
  & exact & structural (SU(3) Weyl group)\\
6 & $\Delta n\neq 2$
  & exact & structural (unique integer)\\
7 & $\theta_{\mathrm{QCD}}\neq 0$
  & $>10^{-10}$ & nEDM at $10^{-28}\,e\!\cdot\!\mathrm{cm}$\\
8 & Proton decays
  & any event & Hyper-K, DUNE ($\tau>10^{35}\,$yr)\\
9 & 4th generation found
  & any signal & LHC Run~3+\\
10 & $\delta_{\mathrm{EW}}>50\,$ppb
  & upper bound & future 2-loop calculation\\
\bottomrule
\end{tabular}
\end{center}

\noindent
Criteria 1--3 are testable with \emph{existing} experiments.
Criteria 4--6 are structural and already verified.
Criteria 7--9 are testable within 5--10 years.
Criterion~10 requires a dedicated calculation.

The criteria are \emph{correlated}: if criterion~1 fails,
then \emph{either} criterion~4, 5, or~6 must also fail, producing
a distinctive multi-prediction failure pattern. A random framework
cannot satisfy all ten criteria simultaneously ($p<10^{-20}$ under
the null hypothesis; Appendix~\ref{sec:statistics}).
